---
title: "Course 3 - Data Cleaninf in R"
output: html_notebook
---

Quiz - 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

How many properties are worth $1,000,000 or more?

Answer:

```{r}
setwd("C:\\Users\\Ishwa\\Desktop\\DataScience\\R\\Getting and Cleaning Data")
getwd()
housing <- read.csv("Idaho Housing Data.csv")
names(housing)
summary(housing)
head(housing$VAL)
length(na.omit(housing[housing$VAL==24,"VAL"]))

```
Quiz - 2

Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?

Answer: Tidy data has variable values that are internally consistent.

```{r}
summary(housing$FES)
```

```{r}
library("xlsx")
dat <- read.xlsx("Natural Gas Aquisition Program.xlsx", sheetName='NGAP Sample Data', , rowIndex=(18:23), colIndex=(7:15))
dat
sum(dat$Zip*dat$Ext,na.rm=T)
```
Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?
```{r}

library(XML)
library(data.table)

library("methods")
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"

doc <- xmlTreeParse(sub("s","",fileUrl), useInternal=TRUE)
rootNode<- xmlRoot(doc)
length(xpathSApply(rootNode,"/response//row[zipcode=21231]",xmlValue))


```
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object

The following are ways to calculate the average value of the variable pwgtp15 broken down by sex. Using the data.table package, which will deliver the fastest user time?



```{r}
?fread
DT <- fread("Idaho Housing Data-1.csv", data.table = T)
class(DT)
system.time(sapply(split(DT$pwgtp15,DT$SEX),mean))
system.time(tapply(DT$pwgtp15,DT$SEX,mean))
system.time(DT[,mean(pwgtp15),by=SEX])
system.time(mean(DT$pwgtp15,by=DT$SEX))
system.time({mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)})
system.time({rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]})

```
```{r}
mean(DT$pwgtp15,by=DT$SEX)
sapply(split(DT$pwgtp15,DT$SEX),mean)
tapply(DT$pwgtp15,DT$SEX,mean)
DT[,mean(pwgtp15),by=SEX]

?mean
```

