---
title: "Getting and Cleaning Data - Week3"
output: html_notebook
---
Question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

Create a logical vector that identifies the households on greater than 10 acres who sold more than $10,000 worth of agriculture products. Assign that logical vector to the variable agricultureLogical. Apply the which() function like this to identify the rows of the data frame where the logical vector is TRUE.

which(agricultureLogical)

What are the first 3 values that result?


```{r}
# Check the working directory and load the file
getwd()
house_Data <- read.csv("American Community.csv")

# Explore the input data
summary(house_Data)
names(house_Data)
head(house_Data$ACR)

# Filter the data as per the requirement above
agricultureLogical<- (house_Data$ACR==3&house_Data$AGS==6)
which(agricultureLogical)

```
Question 2

Using the jpeg package read in the following picture of your instructor into R

https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg

Use the parameter native=TRUE. What are the 30th and 80th quantiles of the resulting data? (some Linux systems may produce an answer 638 different for the 30th quantile)

```{r}

# Install the required packages
install.packages("jpeg")
library(jpeg)
library(help=jpeg)

# Load the JPEG image file and calculate the specified quantile values 
jpeg_val <- readJPEG("getdata_jeff.jpg", native = TRUE)
quantile(jpeg_val, c(0.30, 0.8))

```
Question 3

Load the Gross Domestic Product data for the 190 ranked countries in this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv

Load the educational data from this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv

Match the data based on the country shortcode. How many of the IDs match? Sort the data frame in descending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame?

Original data sources:

http://data.worldbank.org/data-catalog/GDP-ranking-table

http://data.worldbank.org/data-catalog/ed-stats

```{r}

# Load the required packages
library(dplyr)

# Load the GDP data, take care of the title , header lines, and the additional data at the bottome of the file
GDP_data <- read.csv("getdata_data_GDP.csv", header=FALSE, skip=5, sep=",",  nrows=190, colClasses = c("character", "char(acter", "NULL", "character", "character", rep("NULL",5)))
names(GDP_data) <- c("CountryCode","Ranking","Economy", "GDPValue")


# Load the edu data
edu_data <- read.csv("getdata_data_EDSTATS_Country.csv")

# Perform inner_join of GDP and Edu data on CountryCode
GDP_Edu <- inner_join(GDP_data, edu_data, by="CountryCode" )

# Order the Data in the descending value of GDP ranking
ord_GDP_edu <- arrange(GDP_Edu, desc(as.numeric(Ranking)))

# Find the total number of rows and the value in the 13th row
ord_GDP_edu
head(ord_GDP_edu, 20)
tail(ord_GDP_edu)

```
Question 4

What is the average GDP ranking for the "High income: OECD" and "High income: nonOECD" group?

```{r}

# Using the same merged data from above fins the avg ranking for each income group
GDP_Edu %>% select(Ranking, Income.Group) %>% group_by(Income.Group) %>% summarise(AvgRanking = mean(as.integer(Ranking), na.rm=TRUE))

```

Question 5

Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries

are Lower middle income but among the 38 nations with highest GDP?

```{r}
# Cut the Merged data set into five quantile value of ranking
Quan_inc_Grp <- GDP_Edu %>% select(CountryCode, Ranking, Income.Group) %>% mutate(QuantileGrp= findInterval(as.integer(Ranking), quantile(as.integer(Ranking), na.rm=TRUE)))
Quan_inc_Grp

# Create the Table of Income group and quantile group
table(Quan_inc_Grp$Income.Group, Quan_inc_Grp$QuantileGrp)

# Filter out rows for lower middle income
lower_middle <- Quan_inc_Grp[(Quan_inc_Grp$Income.Group== "Lower middle income") ,]

# Filter out the rows of first 38 countries as per GDP ranking
High_38 <- tail(ord_GDP_edu, 38)

# Find the Intersection of the above two group
intersect(High_38$CountryCode, lower_middle$CountryCode)

```

